### 2023-04-24 paper.tex
minor

To test our DMR detection approach, we selected oligodendrocytes and NSCs from healthy wild type mice of \citet{kremer_scnmt} and ran \texttt{scbs diff} with default parameters.
For GO enrichment analysis, DMRs with an adjusted p-value $<0.01$ were uploaded to GREAT \citep{mclean2010great} with association rules basal plus extension, 0~bp upstream, 20~kb downstream, 1~Mbp max extension, curated regulatory domains included.

>>>>

To test our DMR detection approach, we selected oligodendrocytes and NSCs from healthy wild type mice of \citet{kremer_scnmt} and ran \texttt{scbs diff} with default parameters.
For GO enrichment analysis, DMRs with $p^\text{adj}<0.01$ were uploaded to GREAT \citep{mclean2010great} with the association rule "basal plus extension, 0~bp upstream, 20~kb downstream, 1~Mbp max extension, curated regulatory domains included".
